\section{Learning The Frameworks}

Haskell is very different than any language that I have used before, coming from an Object Oriented Background and being used to languages like Python, Java, and PHP. To ensure that my lack of knowledge of Haskell does not give too much of an advantage to Django, I read the book ``Haskell Programming from First Principles'' \parencite{haskellBook}. I used this book to get a general understanding of Haskell and the principles of Functional Programming. After a few weeks of reading through the book, I started reading ``Developing Web Applications with Haskell and Yesod'' \parencite{yesodBook}, a tutorial for the Yesod framework written by the original developer for Yesod, Michael Snoyman. After going through some of the Yesod book, I started to develop my twitter clone in Yesod. Developing the website, referring to the books when I needed to, and getting help on some concepts that I was struggling to learn from my tutor, greatly improved my knowledge of both Haskell and Yesod in a short amount of time.

I was already familiar with the Python language before starting this project, and being familiar with Python is one of the reasons that I chose the Django framework. To learn the basics of Django, I went through the tutorials available on the Django website \parencite{djangoIntroDocs}. This introduction guided you through writing a simple Django app, teaching you some of the basic concepts of the Django.

One thing that I noticed straight away is that, because of the high popularity of the Django web framework, if I needed any help, I could just type my query into a search engine, and most likely, someone else has had the same problem which has already been resolved in a forum post. This is in contrast to Yesod, where most of the time, if I encounted any difficulties, I would have to go through the documentation to try and find a solution. The popularity of Django does give it an advantage in this respect, any problem you come across has most likely already been encountered and resolved by another person. However, the documentation of Yesod is excellent in my opinion, and most problems I have come across were resolved rather quickly. I have also recently discovered that Yesod has an IRC channel which I plan to use if I encounter an error that I am having difficulty solving in the future.
