\section{Meeting 12 - 19th April 2018}

\subsection{Meeting Notes:}
Report draft, hand in by this weekend.

Book in a meeting on Tuesday to discuss the report.

Simulate mistakes and see how the haskell compilers help

Argue against how the compiler may make you write unnecessary code

\begin{itemize}
  \item{Haskell version, I couldn't do something like if not null, ignore the block}
  \item{You can try to use an undefined and force an exception}
  \item{You can do something like "Error - (loc) shouldn't happen"}
\end{itemize}

Type safety saved a lot of time with checking variable types

But people like python because of the lack of type checking

It may be faster to ignore types when developing but it could cause problems later on

In Yesod, there's types for entity Ids, and if the entity Id does not exist, it will 404

Think about seperating language vs framework

For this report, it's more useful to focus on the framework, but think about anything to do with the language

For example, static type checking is to do with Haskell rather than Yesod

In the yesod-test package, you can use HTML selectors. That makes testing static content easy.

Django, you can test HTML page but selectors are not implemented. (If html page contains this string).

If you have time after getting the report done...

Load testing, deploy both apps to the same environment. Is there a tool for it. Send 
multiple queries from multiple machines, time responses.

If no tool, you can try requests from just your own machine.
If you can't get it on Heroku, set up a VM.

Test the ease of deployments for both frameworks. Test the actual production mode, not dev mode.
