\section{Meeting 10 - 15th February 2018}

\subsection{Meeting Notes:}
Created AJAX functionality for getting messages

Resolved issue with using single template for profile by declaring the form stuff even if isCurrentUse is false, this is fine

\subsubsection{What needs to be done}

Add more tests this weekend for both frameworks. Does Haskell's type checking mean we need fewer tests compared to Python?

\subsubsection{What to look at for evaluation}

Evaluate:
\begin{itemize}
	\item{The ease of writing tests}
	\item{In python, you need lots of testing because there's no static type checking}
	\begin{itemize}
    	\item{Does this mean you need less tests in Haskell}
    	\item{Does this mean tests are easier to write in Haskell, or in Python because tests are more important in Python so they'd be easier to use}
	\end{itemize}
	\item{What types of tests are important in the haskell world}
	\item{Some tests are unneeded for Haskell}
	\item{Is it cheaper to build a bullet proof app in Haskell or Python, maintainability? etc}
\end{itemize}

Amount of users in Django makes it easier to find problems that others have experineced

Amount of users in Django means more tools for Django but this is improving on the Haskell on the side

The Yesod book written by the creator of Yesod is pretty good

Some of the problems written by people using Yesod are more detailed, users are probably more experienced in the programming world? more academic?

Evaluate the ease of adding a new feature after the site is complete

Evaluate how quick it is to debug something

Built in compiler and type checking in Haskell is very useful when debugging

Evaluate page load speeds, is Python slower because it runs the interpreter every time?

Scalability if you can

Some quantitative data?

Explain to the reader why some things make a big difference
\begin{itemize}
    \item{How long it takes to get a reliable application}
    \begin{itemize}
        \item{Length of tests? Number of tests? Instances where types catch important errors? These are very useful}
        \item{Times where the type checking or other similar features got in your way?}
        \begin{itemize}
            \item{E.g. profile page was easier to code in Python, this was because of Haskell checking the scoping}
		\end{itemize}
	\end{itemize}
\end{itemize}