\section{Software Development}

This section records the development lifecycle of the Django and Yesod sites. More detailed commit messages
can be found by running a \textit{git log} on the git repo for both sites.

\subsection{Yesod Site}

\subsubsection{1st November 2017}
Created a basic homepage and a vagrantfile.

\subsubsection{23rd November 2017}
Implemented Login and Signup functionality

\subsubsection{11th December 2017}
Created a profile page

\subsubsection{14th December 2017}
Implemented message creation functionality and added some tests

\subsubsection{15th February 2018}
Modified profile page to retrieve messages using AJAX

\subsubsection{19th March 2018}
Implemented functionality to show other registered users on the profile page

\subsubsection{20th March 2018}
Basic functionality to follow users implemented

\subsubsection{21st March 2018}
Refactor profle page and follow functionality to use type safe URLs

\subsubsection{22nd March 2018}
Added functionality to allow users to follow eachother through normal usage of the site.
Previously, users had to type in a URL to follow a user

\subsubsection{31st March 2018}
Refactored profile page. Separated pages used for logged in and anonymous users, reducing
complexity. Refactoring also increased use of type safe URLs in the profile page and
when posting messages.

\subsubsection{1st April 2018}
Updated stack resolver to latest point release for current resolver, ensuring we have
the latest compatible updates for our packages. Fix some bugs and add tests.

\subsubsection{2nd April 2018}
Added tests for all route handlers and integrate tests with Travis CI.

\subsubsection{4th April 2018}
Implemented search functionality

\subsubsection{5th April 2018}
Tested the search functionality

\subsubsection{6th April 2018}
Added latest posted messages to the homepage and used a previously created datatype
to help display posted messages on the frontend.

\subsubsection{7th April 2018}
Added hashtag functionality and fixed some bugs on the profile page. Hashtagged messages
appear on the homepage.

\subsubsection{10th April 2018}
Added yesod prefix to database names so that the Yesod server can be ran the same
time as the Django server.

\subsubsection{11th April 2018}
Removed unneeded visit button on profile page.

\subsubsection{13th April 2018}
Improved ordering of messages posted by other uses on your feed.

\subsection{Django Site}

\subsubsection{9th November 2017}
Created the homepage and a vagrantfile.

\subsubsection{14th November 2017}
Implemented login and signup functionality

\subsubsection{15th November 2017}
Refactored authentication functionality to use Django's built in models rather than custom models.

\subsubsection{31st January 2018}
Implemented profile page and message creation functionality.

\subsubsection{10th April 2018}
Downgrade Django bootstrap version to bootstrap 3. This is the version used by Yesod so using
version 3 reduces the amount of template work to do which does not provide much insight
into the benefits of either framework.

Implemented breadcrumbs and a base template file that all other template files use.

\subsubsection{11th April 2018}
Added AJAX functionality to the profile page.

\subsubsection{12th April 2018}
Completed the profile page and added search functionality

\subsubsection{13th April 2018}
Added tests and fixed any bugs discovered. Latest message and hashtagged messages added to the homepage.
